Scenario 2 - MPX in the EU

### 2022-11-07 MS3.Rmd
Created data dictionary

```{r packages}
library(ggplot2)
library(tidyverse)
library(readr)
library(lubridate)
library(stringr)
library(readxl)
```
```{r}
euro_mpx_cases <- read_csv("files/euro_mpx_cases.csv")
euro_census_stats <- read_csv("files/euro_census_stats.csv")
euro_pop_denominators <- read_csv("files/euro_pop_denominators.csv")
world_country_regions <- read_csv("files/phw251_projectdata-d6f7578ccda8b47b98f4ab30005bbd76acf496ec/world_country_regions.csv")
```
\newpage

@@

```{r}
#Upload the Data Dictionary for the central data-frame: "euro_mpx_cases"
Data_Dictionary <- read_excel("~/PHW251_Fall2022/251/MS3_data_dictionary.xlsx")
Data_Dictionary
```

>>>>

```{r packages}
library(ggplot2)
library(tidyverse)
library(readr)
library(lubridate)
library(stringr)
library(readxl)
library(kableExtra)
```
```{r}
euro_mpx_cases <- read_csv("files/euro_mpx_cases.csv")
euro_census_stats <- read_csv("files/euro_census_stats.csv")
euro_pop_denominators <- read_csv("files/euro_pop_denominators.csv")
world_country_regions <- read_csv("files/world_country_regions.csv")
```
\newpage

@@

```{r}
#Create the Data Dictionary

names <- names(euro_mpx_cases)
data_type <- sapply(euro_mpx_cases,class)
description <- c("Reporting time period with the floor month", #floor_month
                 "Abbreviation of Country", # CountryCode
                 "The current population of the country for 2022", # country_pop_2022
                 "Total confirmed MPX cases grouped by month", # cases_grouped_monthly
                 "The designated region the country is located", # EU_region
                 "Sum of the four months per country code", # sum_region_cases
                 "The Sum of population 0-1000", # 0-1000
                 "The Sum of population 1000-9999", # 1000-9999
                 "The Sum of population 10000-99999", # 10000-99999
                 "The Sum of population 100000-199999", # 100000-199999
                 "The Sum of population 200000-499999", # 200000-499999
                 "The Sum of population 500000-999999", # 500000-999999
                 "The Sum of population GE1000000" # GE1000000
)

data_dic <- as.data.frame(cbind(names, data_type, description)) %>% 
  select(-names)

kable(data_dic,
      col.names = c("Data Type", 
                    "Description"),
      caption = "Data Dictionary"
      ) 
```
